### 2020-01-05 misc/solutions/papa-sols.tex
Fatou's lemma question

>>>>

\proclaim 8. Put $f_n = \chi_E$ if $n$ is odd, $f_n = 1 - \chi_E$ if $n$ is even. What is the relevance of this example to Fatou's lemma?

This gives an example of strict inequality arising. Let $X$ be a measure space such that $\mu(X) = 1$ and let $E\subseteq X$ be such that $\mu(E) = 2/3$. Then
$$\int_X \liminf_{n\rightarrow\infty} f_n \d\mu = \int_X 0 \d\mu = 0,$$
while on the other hand
$$\liminf_{n\rightarrow\infty} \int_X f_n\d\mu = \int_X 1 - \chi_E \d\mu = \int_X 1 \d\mu - \int_X \chi_E \d\mu = \mu(X) - \mu(E) = {1\over 3},$$
and we have $0<1/3$.
